Analysis of split plot design using MCMCglmm

### 2017-08-25 README.Rmd
Clean up R package
Package is now fully functional and passes R CMD checks

_pkgdown_ site is now included as well.

---
output:
  md_document:
    variant: markdown_github
---

@@

The goal of rice.awd.shb is to ...

@@

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

---
output: github_document
---

@@

The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect pests and sheath blight disease in rice paddies.

## Study

**Objective:** Study the effects of different water and nitrogen managements on sheath blight of rice

**Project PI:** Dr. Adam H Sparks  and Dr. Buyung AR Hadi

**Staff:**

  * Dr. Nancy P. Castilla (2016)

  * Mr. Michael Noel (2015)

******

### 1. SCHEDULE

IRRI Dry Season (2)

 * 2015 (December 2014 – April 2015)

 * 2016 (January 2016 - May 2016)

### 2. METHODOLOGY

**Experimental Design: Split-plot**

  * Main plot : Water management (2)

    * W1 – Alternate Wetting and Drying (AWD)

    * W2 – Flooded/Farmer’s Practice

  * Sub-plot : Nitrogen management (5)

    * 2015

      * N0 – 0 kg/ha

      * N1 – 100 kg/ha (farmer’s practice – based from J. Bigornia research)

      * N2 – 120 kg/ha (IRRI practice – based from L. Willocquet research)

    * 2016

      * N3 – 60 kg/ha

      * N4 - 180 kg/ha

  * Replication: Four (4)

  * Plot Sizes (2015)

    * Main plot size: 12m x 12m (144 sq m)

    * Sub-plot size: 5m x 5m (25 sq m)

    * Replication size: 12m x 24m (288 sq m)

    * Buffer: 1m per sub plot

    * Experiment size: 1,152 sq m

  * Plot Sizes (2016)

    * Main plot size

      * Block 2007: 21m x 20.5m (412.5 sq m)

      * Block 2008: 20.25m x 21.6m (437.4 sq m)

    * Sub-plot size

      * Block 2007: 21m x 10.25m (215.25 sq m)

      * Block 2008: 20.25m x 10.8m (218.7 sq m)

    * Replication size:

      * Block 2007: 42m x 20.5m (861 sq m)

      * Block 2008: 40.5m x 21.6m (874.8 sq m)

    * Buffer: 0.5m per sub plot

    * Experiment size: 3471.6 sq m

******

**Disease Rating Scale**

Disease was rated using an ordinal scale for field evaluation of sheath blight (S Savary & N Castilla).

* **Rating Scale - Severity (%)**

    * 0 - 0,

    * 1 - 1%,

    * 2 - 5%,

    * 3 - 15%,

    * 4 - 50%,

    * 5 - >50%

******

**Nitrogen Management Rates**

<table width = "500">
<tr>
  <th rowspan = "2">Nitrogen<br>treatment</th>
  <th rowspan = "2">Year</th>
  <th rowspan = "2">Total N<br>(kg/ha)</th>
  <th colspan = "4">Application Amount (kg/ha)</th>
</tr>
<tr>
  <th>Basal</th>
  <th>Tillering</th>
  <th>Panicle<br>Intitiation</th>
</tr>
<tr>
  <td>N0</td>
  <td>2015</td>
  <td>0</td>
  <td>0</td>
  <td>0</td>
  <td>0</td>
</tr>
<tr>
  <td>N100</td>
  <td>2015</td>
  <td>100</td>
  <td>60</td>
  <td>20</td>
  <td>20</td>
</tr>
<tr>
  <td>N120</td>
  <td>2015</td>
  <td>120</td>
  <td>60</td>
  <td>30</td>
  <td>30</td>
</tr>
<tr>
  <td>N60</td>
  <td>2016</td>
  <td>60</td>
  <td>30</td>
  <td>30</td>
  <td>0</td>
</tr>
<tr>
  <td>N180</td>
  <td>2016</td>
  <td>180</td>
  <td>60</td>
  <td>60</td>
  <td>60</td>
</tr>
</table>

## Resources

### glmm split plot analysis

http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html

http://www.stat.wisc.edu/courses/st572-larget/Spring2007/handouts16-4.pdf

http://www.maths.bath.ac.uk/~jjf23/mixchange/split.html

### Using MCMCglmm

http://www.maths.bath.ac.uk/~jjf23/mixchange/onewayanova.html

http://www.maths.bath.ac.uk/~jjf23/mixchange/split.html#mcmcglmm

https://github.com/tmalsburg/MCMCglmm-intro

### General GLMM in R

http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html

@@

**Data:** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
